\documentclass[9pt, a4paper, twocolumn]{oblivoir}
\usepackage{fapapersize}
    \usefapapersize{210mm,297mm,20mm,20mm,25mm,25mm}
\usepackage{fancyhdr}
\pagenumbering{gobble}
\fancypagestyle{firststyle}
{
    \pagestyle{fancy}
% \fancyhf{}
% \rhead{Overleaf}
\lhead{\textbf{\LARGE Exercises}}
% \rfoot{Page \thepage}

}

\pagestyle{firststyle}
\setlength{\headheight}{12pt}
\addtolength{\topmargin}{-0.334pt}
\begin{document}

    \begin{itemize}[\null]
        \item 다음 빈칸에 들어갈 말로 가장 적절한 것은? % 2011 수능 29
        
        It is a fundamental mistake to imagine that when we see
the non-value in a value or the untruth in a truth, the value
or the truth ceases to exist. It has only become relative.
Everything human is relative, because everything rests on
an inner polarity; for everything is a phenomenon of energy.
Energy necessarily depends on a pre-existing polarity, without
which there could be no energy. There must always be high
and low, hot and cold, etc., so that the equilibrating
process \textemdash~which is energy \textemdash~can take place. Therefore the
tendency to deny all previous values in favor of their
opposites is just \rule{5cm}{0.1mm}. And in so
far as it is a question of rejecting universally accepted and
indubitable values, the result is a fatal loss. \\
\begin{flushright}
   {\small$*$  polarity: 극단 $**$ phenomenon: 현상 
    $***$ equilibrate: 평형하게 하다.}
\end{flushright}
{\small %}
① another way of pursuing relativeness in human affairs\\
② as desirable as the tendency to accept all those values\\
③ as much of an exaggeration as the earlier onesidedness\\
④ the one and only way of approaching the ultimate truth\\
⑤ to admit the presence of energy derived from an inner polarity\\        
}
\newpage
    \end{itemize}

    \begin{enumerate}
        \item Even though you were looking at the words, you apparently were not paying attention. There is a mental aspect of
        attention that involves processing that can occur independently of eye movements.
        \item Relaxing in a comfortable chair, putting on some soothing sounds, and reading something light and entertaining are all
        good methods to get ready for some restful sleep.
        \item We’ve emphasized that hereditary factors are critical in determining which children can look forward to being out-
        standing, and perhaps even elite, athletes.
        \item Readers would see in his poems a vibrant cultural performance, an individual springing from the book with tremendous
        charisma and appeal.
        \item Only this kind of whole-hearted interest will give the mind the energy needed to see what is new and different,
        especially when the latter seems to threaten what is familiar, precious, secure, or otherwise dear to us.
        \item Similarly, corn in Latin America is traditionally ground or soaked with limestone, which makes available a
        B vitamin in the corn, the absence of which would otherwise lead to a deficiency disease.
        \item Composers describe their private world through the use of sound. Making such a description concrete and
        detailed requires not just inspiration but certain practical tools and skills.
        \item Furthermore, it is the behaviour of some tourists, and the structure and development of tourism itself, that often generate negative attitudes within the host community. 
        \item The increased interest in the individual and in satisfying the human senses that was characteristic of the age
        grew stronger in the fifteenth and sixteenth centuries and has remained important ever since.
    \end{enumerate}
\end{document}
