\documentclass[a4paper, twocolumn]{oblivoir}
\usepackage{fapapersize}
    \usefapapersize{210mm,297mm,20mm,20mm,25mm,25mm}
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
\usepackage{fancyhdr}

\pagenumbering{gobble}
\fancypagestyle{firststyle}
{
    \pagestyle{fancy}
% \fancyhf{}
% \rhead{Overleaf}
\lhead{\textbf{\LARGE Sentences}}
% \rfoot{Page \thepage}

}
\fancypagestyle{secondstyle}
{
    \pagestyle{fancy}
% \fancyhf{}
% \rhead{Overleaf}
\lhead{\textbf{\LARGE Sentences and Readings}}
% \rfoot{Page \thepage}

}
\fancypagestyle{thirdstyle}
{
    \pagestyle{fancy}
% \fancyhf{}
% \rhead{Overleaf}
\lhead{\textbf{\LARGE Readings}}
% \rfoot{Page \thepage}

}


\begin{document}
    \textbf{(1 $\sim$  21)} 주어진 문장을 해석해보시오. \\
    해석이 어려운 경우에는 주어를 S, 동사를 V, 보어를 C, 목적어를 O로 표시하고, 
    필수 문장 성분이 아닌 수식어구는 M으로 표시하여 수식하는 대상을 표시해보시오. 
    \thispagestyle{firststyle}
    \section{}
    His neighbor Aristotle also saw the object and suggested it could be a weather balloon.
    
    \section{}
    If you could help me find him or if anyone has any information they can give me I would greatly appreciate it.

    \section{}
    Before doing the real thing, practice on scrap paper to figure out the perfect amount of paint and pressure needed to make flawless stamps.

    \section{}
    The banned performance-enhancing drug nandrolone was detected in eight players last year.

    \section{}
    The handsome prince fell in love with the reflection of himself in the mirror.

    \section{}
    One may work diligently during the cooler part of the day, but when the sun is highest, rest in necessary.

    \section{}
    In my own travels, for example, had I taken packaged tours I never would have had the eye-opening experiences that have added so much to my appreciation of human diversity.

    \section{}
    Allocated a larger budget, the film could have been much better than it was, but it does provide decent entertainment.

    \section{}
    When they “multitask,” they switch back and forth, alternating their attention until both tasks are done.

    \section{}
    It is tempting to think ``if only he had managed to walk to the village, he would have been rescued.''

    \section{}
    Organizational successes and failures are often attributed to effective or ineffective leadership, although followers may have been the true reason behind the outcome.
    
    \section{}
    He is considered to have been the first person that conducted historical work in the United States.

    \section{}
    Few of us are bothered by such restrictions, for our socialization is so thorough that we usually want to do what our roles indicate is appropriate.

    \section{}
    At the core of this lie the concepts of trust and obligation, which enable individuals to cooperate in groups to solve the problems of survival and successful reproduction in more efficient ways.
    \pagebreak
    \section{}
    They either believe they have unlimited time, thinking that they will have more time tomorrow to get something done, or they underestimate how much time they really do have.

    \section{}
    At the heart of individualism lies the belief that each individual person composes the center of one’s universe.

    \section{}
    He spent hours collecting data that he thought would help him improve.

    \section{}
    Furthermore, it is the behaviour of some tourists, and the structure and development of tourism itself, that often generate negative attitudes within the host community.
    \thispagestyle{secondstyle}
    
    \section{}
    Only if this duty of confidentiality is respected will people feel free to consult lawyers and provide the information required for the lawyer to prepare the client’s defense.

    \section{}
    Create an environment in which your children know that you are with them in their efforts, rather than looking to criticize them.

    \section{}
    Psychologist Mihaly Csikszentmihalyi suggests that the common idea of a creative individual coming up with
    great insights, discoveries, works, or inventions in isolation is wrong.

    \pagebreak
    \begin{enumerate}
        \item 다음 글의 요지로 가장 적절한 것은?
        
        Despite numerous studies on the influence of mediated
        agendas on politics, most studies examine text only --- as if
        media only deliver words. These studies looked at how
        reporters, analysts, and commentators verbally describe and
        criticize the candidates. But they often neglect another
        important source of influence: visuals. As some
        communication scholars said, “Stories are often complex
        combinations of visual and verbal content ⎯ all too often the
        visual information is so powerful that it overwhelms the
        verbal.” The challenge of tackling visuals to examine their
        influence is multifaceted. The difficulties of gathering and
        coding visual data and of attributing impact to specific parts
        of images have no doubt caused veritable scholars to shy
        away. But the potential impact of visuals on people’s
        perceptions is simply too important to ignore. Furthermore,
        the importance of understanding both visuals and text in
        tandem cannot be understated. 
        \begin{flushright}
            \small{* veritable: 진정한 ** in tandem: 동시에}
        \end{flushright}
        \begin{enumerate}
            \item visual data are crucial in studies of politics
            \item the opinions of experts have to be investigated completely
            \item programs that reflect various interests are required
            \item excessive visual data can interrupt understanding of studies 
        \end{enumerate}


        \pagebreak
        \thispagestyle{thirdstyle}
    
        \item 다음 글의 주제로 가장 적절한 것은?
        
        In the movie Groundhog Day, a weatherman played by Bill
        Murray is forced to re­live a single day over and over again.
        Confronted with this seemingly endless loop, he eventually
        rebels against living through the same day the same way
        twice. He learns French, becomes a great pianist, befriends
        his neighbors, helps the poor. Why do we cheer him on?
        Because we don’t want perfect predictability, even if what’s on repeat is appealing. Surprise engages us. It allows us to
        escape autopilot. It keeps us awake to our experience. In
        fact, the neurotransmitter systems involved in reward are tied to the level of surprise: rewards delivered at regular,
        predictable times yield a lot less activity in the brain than
        the same rewards delivered at random unpredictable times.
        Surprise gratifies
        \begin{flushright}
            \small{* loop: 고리 ** neurotransmitter: 신경전달물질}
        \end{flushright}
        \begin{enumerate}
            \item people’s inclination towards unpredictability
            \item hidden devices to make a movie plot unexpected
            \item positive effects of routine on human brain function
            \item danger of predicting the future based on the present
        \end{enumerate}
    
        \pagebreak

        \item 빈칸에 들어갈 말로 가장 적절한 것을 고르시오. 
        
        In a culture where there is a belief that you can have
        anything you truly want, there is no problem in choosing.
        Many cultures, however, do not maintain this belief. In fact,
        many people do not believe that life is about getting what
        you want. Life is about doing what you are supposed to do.
        The reason they have trouble making choices is they believe
        that what they may want is not related to what they are
        supposed to do. The weight of outside considerations is
        greater than their \rule{1cm}{0.15mm}. When this is an issue in a
        group, we discuss what makes for good decisions. If a
        person can be unburdened from their cares and duties and,
        just for a moment, consider what appeals to them, they get
        the chance to sort out what is important to them. Then they
        can consider and negotiate with their external pressures.
        \begin{enumerate}
            \item advantages
            \item worries
            \item desires
            \item burdens
        \end{enumerate} 

        

    \end{enumerate}

    


    \pagebreak
    \textbf{정답}
    \begin{enumerate}
        \item (a)
        \item (a)
        \item (c)
    \end{enumerate}


\end{document}