\documentclass[9pt, a4paper,  landscape]{oblivoir}
\usepackage{fapapersize}
    \usefapapersize{210mm,297mm,20mm,20mm,25mm,25mm}
\usepackage{fancyhdr}
% \usepackage{multicol}


\pagenumbering{gobble}
\setlength{\parindent}{0mm}
\setlength{\headheight}{13pt}
\addtolength{\topmargin}{-1.31203pt}
\fancypagestyle{firststyle}{%
        \pagestyle{fancy}
        \lhead{\textbf{\LARGE 필수 문장}}
}

\pagestyle{firststyle}

\begin{document}
    \begin{enumerate}
        % unit 1
        \item She is fourteen years old. 
        \item I was in the football club.
        \item They are my classmates.
        \item The library is open from 9 to 5. 
        \item I am a member of the art club.
        % unit 2
        \item I am not a morning person. 
        \item They weren't here yesterday. 
        \item Are Bill and Sue neighbors?
        \item He is not good at Korean.
        \item Were you okay without me? 
        \item It was not his watch.
        \item I am not worried. 
        \item Mary was not there then.
        % unit 3
        \item I study English only two times a week.
        \item Ms.~Jones always carries her laptop with her.
        \item Todd fixees his computer by himself. 
        \item Does Ted cook well?
        \item Did your sisters enjoy my food? 
        \item He doesn't work hard. 
        \item He lives in a small village of Thailand. 
        \item My brother doesn't like old movies. 
        \item Did you hear the sound? 
        \item She rides her bicycle every Saturday. 
        % concept 7 8
        \item Mike dropped his pencil.
        \item She wasn't able to stop crying. 
        \item Jack played with his friends all day long.
        \item  I didn't meet him yesterday.
        \item Did he travel to Canada last year?
        \item He helped me with my homework. 
        \item We arrived at the market at 10'o clock.
        % concept 9 10
        \item I didn't do my homework last night. \\ I did my homework last night. 
        \item She gets up at 7 a.m.~every day.
        \item I lost my watch at the department store
        \item It will be cloudy tomorrow.
        \item I am not going to go to Japan. 
        \item Will you come to my house this evening?
        \item Mike will feed the cat. 
        \item She exercises every day.
        \item Earth goes around the sun. 
        \item I saw foxes at the zoo.
        %  concpet 11 12
        \item I was driving to the book store. 
        \item He is singing in the room. 
        \item He reads a book. \\ He is reading a book. 
        \item Do you want to be kind? 
        \item Is everything going well? 
        \item They were carrying many things in their hands. 
        \item She was helping her mother. 
        \item The escalator is not working. 
        % concept 13 14 
        \item I can play (the) violin.
        \item May I use the paper here? 
        \item Horses cannot see right in front of their noses. 
        \item It may be cloudy today. 
        \item Can you see the light in the sky? 
        \item You must do your best. 
        \item Students don't have to go to school today because it's Saturday.
        \item We have to wait for the green light.
        \item You sohuld finish your homework.
        \item I can write my name in English. 
        \item He won't have dinner tonight. 
        \item You must turn off your ceel phone.
        \item People and plants cannot live in as hot a place as this. 
        % concept 15 16 
        \item He drank a cup of milk. 
        \item You should brush your teeth three times a day.
        \item Our team won the game. 
        \item He talked to me about himself. 
        \item I took a picture of flowers. 
        \item Their books were burned down sadly.
        \item Its name wil be Jimin. 
        \item They can run away from their enemies easily. 
        % \item concept 17 18 
        \item What time is it? \textendash~It is 9 p.m.
        \item How far is it? \textendash~It is about 100 meters. 
        \item Will it snow tomorrow? 
        \item It gets dark early in (the) winter.
        \item My sister bought me a cap, but I lost it. 
        \item I'm looking for a hat, could you show me one? 
        \item I watched a movie yesterday. I enjoyed it.
        \item These sweaters are too old. Let's buy new ones.
        \item It doesn't snow much in Busan. 
        \item Which one do you like the most? 
        \item I have to backpacks. I like the blue one. 
        \item It rains a lot in my country.
        
    \end{enumerate}
\end{document}